The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd
Add comment on how to visualise topics per docs

```{r setup}
#| echo: false
#| warning: false
#| message: false

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                       # Managing paths
  # TODO remove reshape2 if `melt()` is replaced by`pivot_longer()`
  "tidyverse", "reshape2", "widyr", "readxl",   # Data manipulation and visualisation
  "furrr",                                      # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",                # Text processing and analysis
  "topicmodels", "LDAvis", "tsne",              # Topic modeling
  "tidygeocoder",                               # Working with spatial data
  "igraph", "ggraph"                            # Network analysis and visualization
)

@@

```{r fig-topics-per-doc}

# What is the dominant topic in each document?
N = 20
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- topic_names
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(rownames(topic_prop_examples))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")

>>>>

```{r setup}
#| include: false

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                       # Managing paths
  # TODO remove reshape2 if `melt()` is replaced by`pivot_longer()`
  "tidyverse", "reshape2", "widyr", "readxl",   # Data manipulation and visualisation
  "furrr",                                      # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",                # Text processing and analysis
  "topicmodels", "LDAvis", "tsne",              # Topic modeling
  "tidygeocoder",                               # Working with spatial data
  "igraph", "ggraph", "DiagrammeR"              # Network analysis and visualization
)

@@

```{r fig-topics-per-doc}
#| fig-cap: Topic probability distribution per document

# TODO Replace this with a table containing topics, documents, and theta
#      sorted by theta in decreasing order
# What is the dominant topic in each document?
N = 20
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- topic_names
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(rownames(topic_prop_examples))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")
